Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-02-14 latex/comp_or.tex
mpShims main processes well described

Figure \ref{fig:whip} represents the $n_{\pi(k)}$\/ possible edges $e_{ij}^{\pi(k)}$\/ of $p_i$\/ sorted by $\theta_{ij}^{\pi(k)}$. \emph{Shims}\/ starts with a greedy solution, stopping at the edge with index in $\eta_1[i]$ close to the local optimum (first phase). Then, considering even the edge with the index $\eta_2[i]$, it elaborates different possible complements for this pallet (second phase) and selects the best of these complements (third phase).

{\color{blue} In this work, we included a new phase between the first and the second: a minimization of the CG deviation. An integer programming procedure that helps improve the overall {\it mpShims} results.

$1^{st}$ - Greedy phase

@@

$3^{st}$ - Shims construction

$4^{st}$ - best Shims selection

@@

\begin{algorithm}[H]
	\caption{Mount a greedy solution until the volume limit for each pallet}  \label{alg:mpShims}

@@

		\State Let $G(E^{Q_{\pi(k)}})$ \Comment{the solution comes with some consolidated on board}

@@

		\State $lock \gets$ multi-processing lock \Comment{for shared data among processes to avoid race condition}

@@

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets Greedy(p_i,\ N_{\pi(k)},\ \pi(k),\ nodeTorque,\ G,\ limit,\ lock,\ ts )$
		\State $proc_i.start$
		\EndFor

		\For{$i \gets 1$ to $m$}
		\State $proc_i.join$
		\EndFor

@@

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets getBestShims(p_i,\ N_{\pi(k)},\ \pi(k),\ nodeTorque,\ G,\ surplus,\ lock,\ ts )$
		\State $proc_i.start$
		\EndFor

		\For{$i \gets 1$ to $m$}
		\State $proc_i.join$

@@

		\Return $G(E^{N_{\pi(k)}} \cup E^{Q_{\pi(k)}})$

@@

Line \ref{mpShims:ts} defines the torque surplus ($ts$). For this phase, the solution may generate torque infeasible solutions with doubled torque, which will be repaired by the next phase, the minimization of the CG deviation.

Line \ref{mpShims:minCGdev} presents the procedure to minimize the CG deviation and repair the infeasible greedy solution.

>>>>

{\color{blue}
Figure \ref{fig:whip} represents the $n_{\pi(k)}$\/ possible edges $e_{ij}^{\pi(k)}$\/ of $p_i$\/ sorted by $\theta_{ij}^{\pi(k)}$. \emph{Shims}\/ starts with a greedy solution, stopping at the edge with index in $\eta_1[i]$ close to the local optimum (first phase). Then, considering even the edge with the index $\eta_2[i]$, it elaborates different possible complements for this pallet and selects the best of these complements (second phase).

Although the second phase solves a knapsack problem, an algorithm for solving a bin packing problem was used (the First Fit Decreasing - FFD), and the most profitable bin (shims) was selected. This method was proved to be faster than a dynamic program solution for the knapsack problem.

	In this work, we included a new phase after the first: a minimization of the CG deviation. An integer programming procedure that helps improve the overall {\it mpShims} results.

$1^{st}$ - Greedy phase with torque surplus

@@

$3^{st}$ - Shims construction and best Shims selection

@@

\begin{algorithm}[H]
	\caption{$mpShims$ main process}  \label{alg:mpShims}

@@

		\State Let $G(M,\ Q_{\pi(k)},\ E_{\pi(k)})$ \label{mpShims:g1} \Comment{the initial solution solution}

@@

		\State $lock \gets$ multi-processing lock  \label{mpShims:lock} \Comment{avoid race condition}

@@

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets Greedy(p_i,\ N_{\pi(k)},\ \pi(k),\ nodeTorque,\ G,\ limit,\ lock,\ ts )$   \label{mpShims:greedy}
		\State $proc_i.start$
		\EndFor

		\For{$i \gets 1$ to $m$}
		\State $proc_i.join$ \label{mpShims:join1}
		\EndFor

@@

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets getBestShims(p_i,\ N_{\pi(k)},\ \pi(k),\ nodeTorque,\ G,\ surplus,\ lock,\ ts )$ \label{mpShims:getBestShims}
		\State $proc_i.start$
		\EndFor

		\For{$i \gets 1$ to $m$}
		\State $proc_i.join$ \label{mpShims:join2}

@@

		\Return $G(M,\ N_{\pi(k)} \cup Q_{\pi(k)},\ E_{\pi(k)})$ \label{mpShims:return}

@@

Line \ref{mpShims:g1} the initial solution comes with some consolidated on board, a bipartite graph between pallets and consolidated.

Line \ref{mpShims:ts} defines the torque surplus ($ts$). For the greedy phase, the solution may generate torque infeasible solutions with doubled torque ($2.0$), which will be repaired by the next phase, the minimization of the CG deviation.

Line \ref{mpShims:lock} creates a lock feature for shared data among processes to avoid race condition.

Line \ref{mpShims:greedy} calls the greedy method which updates $p_i$, $N_{\pi(k)}$, $nodeTorque$, and $G$.

Line \ref{mpShims:join1} wait for all $Greedy$ processes to finish.

Line \ref{mpShims:minCGdev} calls the $minCGdev$ method which updates the $nodeTorque$ and $G$. $minCGdev$ minimizes the CG deviation and repairs the greedy solution if it is infeasible.

Line \ref{mpShims:getBestShims} calls the $getBestShims$ method which updates $p_i$, $N_{\pi(k)}$, $nodeTorque$, and $G$.

Line \ref{mpShims:join2} wait for all $getBestShims$ processes to finish.

Line \ref{mpShims:return} returns a complete solution, a bipartite graph between pallets and consolidated or items.
